Generate Frame Measures

### 2022-05-25 data-cleaning/07-generate-frame-measures.Rmd
update from when box wasnt working

```{r}
frame_terms <- box_read("947335700912", read_fun = readr::read_csv)
```

@@

```{r}
# abortion cases
amicus <- box_read("947307207905", read_fun = readr::read_csv) %>% 
  mutate(brief_party = ifelse(id == 861815623586, 1, brief_party))
```

@@

```{r}
box_write(amicus_frames,
           file_name = "amicus-level-frame-measures.csv",
           dir_id = 161199725595)
```

@@

#xlsx::write.xlsx(final, file = "womens_health_cts.xlsx")
decisions <- readxl::read_xlsx("../eda/ab_cases.xlsx", sheet = "dat")
decisions <- decisions %>% 
  mutate(case = str_replace(case, 'v\\.', 'v'),
         case = str_replace_all(case, "(,|’|'|\\)|\\()", ""),
         case = case_when(
           case == "Anders Solicitor of Richland County v Floyd" ~ "Anders v Floyd",
           case == "Ayotte AG of NH v Planned Parenhood of Northern New England" ~ "Ayotte v PP",
           case == "Beal Sec Dept of Public Wel of PA v Doe" ~ "Beal v Doe",
           case == "Bellotti Attorn Gen of MA v Baird 1979" ~ "Bellotti v Baird 1979",
           case == "City of Akron v Akron Center for Rep Health" ~ "City of Akron v Akron Center",
           case == "Colautti Sec of Wel of PA v Franklin" ~ "Colautti v Franklin",
           case == "Doe et al v Bolton Attorn Gen of GA et al" ~ "Doe v Bolton",
           case == "Gonzales AG v Leroy Carhart" ~ "Gonzales v Carhart",
           case == "Gonzales v Planned Parenthood Federation of America" ~ "Gonzales v PP",
           case == "Harris Sec of HHS v McRae" ~ "Harris v McRae",
           case == "Hartigan Attor Gen of IL v David Zbaraz and Allan G Charles" ~ "Hartigan v Zbaraz",
           case == "Hill et al v Colorado" ~ "Hill v Colorado",
           case == "H L v Matheson Gov of UT" ~ "H.L. v Matheson",
           case == "Judy Madsen v Womens Health Center" ~ "Madsen v Womens Health Center",
           case == "Maher Comm of Soc Serv of CT v Roe" ~ "Maher v Roe",
           case == "NOW v Joseph Scheidler 1994" ~ "NOW v Scheidler 1994",
           case == "Ohio v Akron Center for Reproductive Health" ~ "Ohio v Akron Center",
           case == "Planned Parenthood Assoc of Kansas City MO v Ashcroft Attorn Gen of MO" ~
             "PP v Ashcroft",
           case == "Planned Parenhood of SE Penn v Casey" ~ "PP v Casey",
           case == "Planned Parenthood of Central MO v Danforth Attorn Gen of MO" ~ "PP v Danforth",
           case == "Roe et al v Wade District Attorn of Dallas County" ~ "Roe v Wade",
           case == "Rust v Sullivan Sec of HHS" ~ "Rust v Sullivan",
           case == "Joseph Scheidler v NOW 2003" ~ "Scheidler v NOW 2003",
           case == "Scheidler v NOW 2006" ~ "Scheidler v Now 2006",
           case == "Schenck et al v Pro-Choice Network of Western NY" ~
             "Schenck v Pro-Choice Network",
           case == "Stenberg AG of Neb v Leroy Carhart" ~ "Stenberg v Carhart",
           case == "Thornburgh Gov of PA v American College of Obstetricians and Gynecologists" ~
             "Thornburgh v American College of OBGYNs",
           case == "Webster Attor Gen of MO v Reproductive Health Services" ~ "Webster v Reproductive Health Services", 
           case == "Whole Womans Health v Hellerstedt" ~ "WWH v Hellerstedt",
           T ~ case
         )) %>%
  arrange(case)

@@

final %>% 
  janitor::clean_names() %>% 
  left_join(., decisions, by = "case") %>%
  mutate(death = mortality+morbidity) %>% 
  filter(forgauf == 1, fem_win == 0) %>% 
  group_by(case, ddate2) %>% 
  summarize(n = sum(death)) %>% 
  arrange(ddate2)

final %>% 
  janitor::clean_names() %>% 
  left_join(., decisions, by = "case") %>% 
  mutate(illegal_abortion = illegal_abortion+illegal_abortions,
         safe_abortion = safe_abortion + safe_legal_abortion,
         self_abortion = self_abortion+self_abortions+
           self_induced_abortion+self_induced_abortions) %>% 
  select(-id, -brief_party, -word_ct, -sentences, -tokens, -types) %>% 
  group_by(fem_win, forgauf, medauf) %>%
  #summarize(across(where(is.numeric), ~sum(.x)))
  summarize(illegal_abortion = sum(illegal_abortion),
            safe_abortion = sum(safe_abortion),
            self_abortion = sum(self_abortion))
```

>>>>

```{r}
frame_terms <- box_read("947335700912", read_fun = readr::read_csv)
#frame_terms <- read_csv("~/Box/Amicus IV/data/amicus contents - frames/clean-amicus-iv-frame-dictionary.csv")
```

@@

```{r}
# abortion cases
amicus <- box_read("947307207905", read_fun = readr::read_csv) %>% 
  mutate(brief_party = ifelse(id == 861815623586, 1, brief_party))

#amicus <- read_csv("~/Box/Amicus IV/data/processed amicus files/clean-shortened-amicus-text-vars.csv") %>% 
#  mutate(brief_party = ifelse(id == 861815623586, 1, brief_party))
```

@@

```{r}
#box_write(amicus_frames,
#           file_name = "amicus-level-frame-measures.csv",
#           dir_id = 161199725595)
```

@@

decisions <- readxl::read_xlsx("../eda/ab_cases.xlsx", sheet = "dat")
decisions <- decisions %>% 
  mutate(case = str_replace(case, 'v\\.', 'v'),
         case = str_replace_all(case, "(,|’|'|\\)|\\()", ""),
         case = case_when(
           case == "Anders Solicitor of Richland County v Floyd" ~ "Anders v Floyd",
           case == "Ayotte AG of NH v Planned Parenhood of Northern New England" ~ "Ayotte v PP",
           case == "Beal Sec Dept of Public Wel of PA v Doe" ~ "Beal v Doe",
           case == "Bellotti Attorn Gen of MA v Baird 1979" ~ "Bellotti v Baird 1979",
           case == "City of Akron v Akron Center for Rep Health" ~ "City of Akron v Akron Center",
           case == "Colautti Sec of Wel of PA v Franklin" ~ "Colautti v Franklin",
           case == "Doe et al v Bolton Attorn Gen of GA et al" ~ "Doe v Bolton",
           case == "Gonzales AG v Leroy Carhart" ~ "Gonzales v Carhart",
           case == "Gonzales v Planned Parenthood Federation of America" ~ "Gonzales v PP",
           case == "Harris Sec of HHS v McRae" ~ "Harris v McRae",
           case == "Hartigan Attor Gen of IL v David Zbaraz and Allan G Charles" ~ "Hartigan v Zbaraz",
           case == "Hill et al v Colorado" ~ "Hill v Colorado",
           case == "H L v Matheson Gov of UT" ~ "H.L. v Matheson",
           case == "Judy Madsen v Womens Health Center" ~ "Madsen v Womens Health Center",
           case == "Maher Comm of Soc Serv of CT v Roe" ~ "Maher v Roe",
           case == "NOW v Joseph Scheidler 1994" ~ "NOW v Scheidler 1994",
           case == "Ohio v Akron Center for Reproductive Health" ~ "Ohio v Akron Center",
           case == "Planned Parenthood Assoc of Kansas City MO v Ashcroft Attorn Gen of MO" ~
             "PP v Ashcroft",
           case == "Planned Parenhood of SE Penn v Casey" ~ "PP v Casey",
           case == "Planned Parenthood of Central MO v Danforth Attorn Gen of MO" ~ "PP v Danforth",
           case == "Roe et al v Wade District Attorn of Dallas County" ~ "Roe v Wade",
           case == "Rust v Sullivan Sec of HHS" ~ "Rust v Sullivan",
           case == "Joseph Scheidler v NOW 2003" ~ "Scheidler v NOW 2003",
           case == "Scheidler v NOW 2006" ~ "Scheidler v Now 2006",
           case == "Schenck et al v Pro-Choice Network of Western NY" ~
             "Schenck v Pro-Choice Network",
           case == "Stenberg AG of Neb v Leroy Carhart" ~ "Stenberg v Carhart",
           case == "Thornburgh Gov of PA v American College of Obstetricians and Gynecologists" ~
             "Thornburgh v American College of OBGYNs",
           case == "Webster Attor Gen of MO v Reproductive Health Services" ~ "Webster v Reproductive Health Services", 
           case == "Whole Womans Health v Hellerstedt" ~ "WWH v Hellerstedt",
           T ~ case
         )) %>%
  arrange(case)

@@

final %>% 
  janitor::clean_names() %>% 
  left_join(., decisions, by = "case") %>%
  mutate(death = mortality+morbidity,
         health_risk = health_risk+health_risks) %>% 
  filter(forgauf == 1, fem_win == 0) %>% 
  group_by(case, ddate2) %>% 
  summarize(maternal_health = sum(maternal_health), death = sum(death),
            health_risk = sum(health_risk)) %>% 
  arrange(ddate2)

final %>% 
  janitor::clean_names() %>% 
  left_join(., decisions, by = "case") %>%
  mutate(death = mortality+morbidity) %>% 
  filter(medauf == 1, fem_win == 1) %>% 
  arrange(-death) %>% 
  select(case, brief, forgauf, medauf, death, maternal_health)

final %>% 
  janitor::clean_names() %>% 
  left_join(., decisions, by = "case") %>% 
  mutate(illegal_abortion = illegal_abortion+illegal_abortions,
         safe_abortion = safe_abortion + safe_legal_abortion,
         self_abortion = self_abortion+self_abortions+
           self_induced_abortion+self_induced_abortions,
         health_risk = health_risk+health_risks) %>% 
  select(-id, -brief_party, -word_ct, -sentences, -tokens, -types) %>% 
  group_by(fem_win, forgauf, medauf) %>%
  #summarize(across(where(is.numeric), ~sum(.x)))
  summarize(illegal_abortion = sum(illegal_abortion),
            safe_abortion = sum(safe_abortion),
            self_abortion = sum(self_abortion),
            health_risk = sum(health_risk))
```
